### 2015-10-23 trunk/docs/devel.tex
Issue 1405: added new docs directory with content
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2764 40876441-3496-0410-a613-a2fca35b2ae2

A series of tests are provided in the \texttt{./tests} directory. These
are of two types. Unit tests are generally written when units of code
are first introduced to ensure basic operation is error free. Regression
tests are introduced and updated when physical results are validated.
Both are run regularly as the basis of a nightly test procedure, but
they can be run independently, e.g., after adding or changing code.

@@

>>>>

A series of tests are provided in the \texttt{./tests} directory. These
are of two types. Unit tests are generally written when units of code
are first introduced to ensure basic operation is error free. The unit
tests are encoded in an executable linked against the appropriate
\textit{Ludwig} library.
Regression
tests are introduced and updated when physical results are (broadly)
validated. The regression tests use the stand-alone executable for
the appropriate model, and read input files which define the different
tests.
Both are run regularly as the basis of a nightly test procedure, but
they can be run independently, e.g., after adding or changing code.

@@

A number of different scripts are provided for running serial, parallel,
or GPU tests. For each test script, there is the option to run either
the relevant unit tests, or regression tests, or both. For example, to
run both serial unit tests and serial regression tests for the D3Q19
model, invoke
\begin{lstlisting}
./test-serial.sh -u -r d3q19
\end{lstlisting}
in the test directory.
The model selection follows the naming scheme described for compilation
in the previous section.
See the individual scripts for further information on the command line
options.

### 2015-10-23 trunk/docs/lb.tex
Issue 1405: added new docs directory with content
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@2764 40876441-3496-0410-a613-a2fca35b2ae2

@@

For this work, it is more convenient to rewrite these equations
in tensor notation, where Cartesian coordinates ${x,y,z}$ are
represented by indices $\alpha$ and $\beta$, viz
\begin{equation}
\partial_t \rho + \nabla_\alpha (\rho u_\alpha) = 0
\end{equation}
and
\begin{equation}
\partial_t (\rho u_\alpha) + \nabla_\beta (\rho u_\alpha u_\beta)
= -\nabla_\alpha p
+  \eta \nabla_\beta (u_\alpha \nabla_\beta + \nabla_\alpha u_\beta)
+ \zeta \nabla_\alpha (\nabla_\gamma u_\gamma).
\end{equation}
Here, repeated indices are understood to be summed over.
The conservation law is seem better if the forcing terms of the
right hand side are combined in the fluid stress $\Pi_{\alpha\beta}$
so that
\begin{equation}
\partial_t (\rho u_\alpha) +\nabla_\beta \Pi_{\alpha\beta} = 0.
\end{equation}
In this case the expanded expression for the stress tensor is
\begin{equation}
\Pi_{\alpha\beta} = p \delta_{\alpha\beta} + \rho u_\alpha u_\beta 
+ \eta \nabla_\alpha v_\beta + \zeta (\nabla_\gamma v_\gamma)\delta_{\alpha\beta}
\end{equation}
where $\delta_{\alpha\beta}$ is that of Kroneker. Th Navier-Stokes
equations have 10 degrees of freedom (or hydrodynamic modes) being
$\rho$, three components of the mass flux $\rho u_\alpha$, and 6 independent
modes from the (symmetric) stress tensor $\Pi_{\alpha\beta}$.

\subsection{The Distribution Function and its Moments}

In lattice Boltzmann, the density and velocity of the continuum fluid
are replaced by their discrete counterparrts, the distribution function
$f_i(\mathbf{r}; t)$ and the discrete velocity space $c_{i\alpha}$.
It is possible to relate the hydrodynamic modes to distribution
function via its moments, so
\begin{equation}
\rho = \sum_i f_i,  \,
\rho u_\alpha = \sum_i f_i c_{i\alpha},  \,
\Pi_{\alpha\beta} = \sum_i f_i c_{i\alpha} c_{i\beta.}
\end{equation}
here, the index of the summation is over the number of discrete
velocities used $n$, which in three dimensions is generally
denoted by D3Q$n$. We restrict our discussion to D3Q15 and
D3Q19 (see below).

In general, the number of modes supported in $n$ and these can
be written as
\begin{equation}
M^a(\mathbf{r};t) = \sum_i m_i^a f_i(\mathbf{r};t),
\end{equation}
where $m_i^a$ is the corresponding eigenvector of the collision
maxtrix (see section blah). For example, if $m_i^a = 1$ then the
mode $M^a$ is the density. Correspondingly, the distribution
function can be related to the modes $M^a$ via
\begin{equation}
f_i() = \sum_a w_i m_i^a M^a() N^a
\end{equation}

\subsubsection{Hydrodynamic modes}

\subsubsection{D3Q15 ghost modes}

\subsubsection{D3Q19 ghost modes}

@@

\subsection{The Collision}

\subsection{External Body Forces}

@@

\subsubsection{Fluctuating ghost modes: D3Q15}

\subsubsection{Fluctuating ghost modes: D3Q19}

\subsection{The Propagation}

\subsection{Solid bodies and Bounce-Back on Links}

@@

\subsubsection{Boundary walls}

\subsection{Model Details}

These are the eigenvalues and eigenvectors of the collision
matrix used for D2Q9

\begin{table}
\begin{tabular}{|l|r|rrrrrrrrr|r|l|}
\hline\hline
$M^a$ & & \multicolumn{9}{c|}{$m_i^a$} & $N^a$  &\\
\hline
$\rho$ & - & 1 &  1 &  1 &  1 &  1 &  1 &  1 &   1 &  1 & 1 &$\mathbf{1}$ \\
\hline
$\rho c_{ix}$ & - & 0 &  1 &  1 & 1 & 0 &  0 & -1 &  1 & -1 & 3 & $c_{ix}$ \\
\hline
$\rho c_{iy}$ & - & 0 & 1 &  0 &  -1 &  1 &  -1 & 1 & 0 & -1 & 3  &$c_{iy}$ \\
\hline
$Q_{xx}$ & 1/3 & -1 &  2 &  2 & 2 & -1 & -1 & 2 & 2 & 2 & 9/2 
& $c_{ix} c_{ix} - c_s^2$ \\
\hline
$Q_{xy}$ & - & 0 &  1 & 0 & -1 & 0 & 0 & -1 & 0 & 1 & 9 & $c_{ix} c_{iy}$ \\
\hline
$Q_{yy}$ & 1/3 & -1 &  2 & -1 & 2 & 2 & 2 & 2 & -1 & 2 & 9/2
& $c_{iy} c_{iy} - c_s^2$ \\
\hline\hline
$\chi^1$ & - &  1 & 4 & -2 & 4 & -2 & -2 & 4 & -2 & 4 & 1/4 & $\chi^1$ \\
\hline
$J_{ix}$ & - & 0 &  4 & 0 & -4 & -2 & 2 & 4 & 0 & -4 & 3/8
& $\chi^1 \rho c_{ix}$\\
\hline
$J_{iy}$ & - & 0 & 4 & 0 & -4 & -2 & 2 & 4 & 0 & -4 & 3/8
& $\chi^1 \rho c_{iy}$\\
\hline\hline
$w_i$ & 1/36 & 16 & 1 & 4 & 1 & 4 & 4 & 1 & 4 & 1 & & $w_i$\\
\hline\hline
\end{tabular}
\end{table}

@@

\begin{table}
\begin{tabular}{|l|r|r|rrrrrr|rrrrrrrr|r|l|}
\hline\hline
$M^a$ & & \multicolumn{15}{c|}{$m_i^a$} & $N^a$  &\\
\hline
$\rho$ & - &
 1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &
1 &$\mathbf{1}$ \\
\hline
$\rho c_{ix}$ & - &
 0 &  1 & -1 &  0 &  0 &  0 &  0 &  1 & -1 &  1 & -1 &  1 & -1 &  1 & -1 &
3  & $c_{ix}$ \\
\hline
$\rho c_{iy}$ & - &
 0 &  0 &  0 &  1 & -1 &  0 &  0 &  1 &  1 & -1 & -1 &  1 &  1 & -1 & -1 &
3  &$c_{iy}$ \\
\hline
$\rho c_{iz}$ & - &
 0 &  0 &  0 &  0 &  0 &  1 & -1 &  1 &  1 &  1 &  1 & -1 & -1 & -1 & -1 &
3  & $c_{iz}$ \\
\hline
$Q_{xx}$ & 1/3 &
-1 &  2 &  2 & -1 & -1 & -1 & -1 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &
9/2  & $c_{ix} c_{ix} - c_s^2$ \\
\hline
$Q_{yy}$ & 1/3 &
-1 & -1 & -1 &  2 &  2 & -1 & -1 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &
 9/2 & $c_{iy} c_{iy} - c_s^2$ \\
\hline
$Q_{zz}$ & 1/3 &
-1 & -1 & -1 & -1 & -1 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &
 9/2 & $c_{iz} c_{iz} - c_s^2$ \\
\hline
$Q_{xy}$ & - &
 0 &  0 &  0 &  0 &  0 &  0 &  0 &  1 & -1 & -1 &  1 &  1 & -1 & -1 &  1 &
9  & $c_{ix} c_{iy}$ \\
\hline
$Q_{yz}$ & - &
 0 &  0 &  0 &  0 &  0 &  0 &  0 &  1 &  1 & -1 & -1 & -1 & -1 &  1 &  1 &
9  & $c_{iy} c_{iz}$ \\
\hline
$Q_{zx}$ & - &
 0 &  0 &  0 &  0 &  0 &  0 &  0 &  1 & -1 &  1 & -1 & -1 &  1 & -1 &  1 &
9  & $c_{iz} c_{ix}$ \\
\hline\hline
$\chi^1$ & - &
-2 &  1 &  1 &  1 &  1 &  1 &  1 & -2 & -2 & -2 & -2 & -2 & -2 & -2 & -2 &
1/2 & $\chi^1$ \\
\hline
$J_{ix}$ & - &
 0 &  1 & -1 &  0 &  0 &  0 &  0 & -2 &  2 & -2 &  2 & -2 &  2 & -2 &  2 &
3/2 & $\chi^1 \rho c_{ix}$\\
\hline
$J_{iy}$ & - &
 0 &   0 &  0 &  1 & -1 &  0 &  0 & -2 & -2 &  2 &  2 & -2 & -2 &  2 &  2 &
3/2 & $\chi^1 \rho c_{iy}$\\
\hline
$J_{iz}$ & - &
 0 &   0 &  0 &  0 &  0 &  1 & -1 & -2 & -2 & -2 & -2 &  2 &  2 &  2 &  2 &
3/2 & $\chi^1 \rho c_{iz}$\\
\hline
$\chi^3$ & - &
 0 &   0 &  0 &  0 &  0 &  0 &  0 &  1 & -1 & -1 &  1 & -1 &  1 &  1 & -1 &
9 & $c_{ix} c_{iy} c_{iz}$ \\
\hline\hline
$w_i$ & 1/72 &
$16$ & 8 & 8 & 8 & 8 & 8 & 8 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 &
 & $w_i$\\
\hline\hline
\end{tabular}
\end{table}

@@

\begin{table}
\begin{tabular}{|l||r|rrrrrr|rrrr|rrrr|rrrr|r||}
\hline\hline
$M^a$ & \multicolumn{19}{c||}{$m_i^a$} & $N^a$\\
\hline
$\rho $ & 1 &  1 &  1 &  1 &  1 &  1 &  1 & 
         1 &  1 &  1 &   1 &  1 &  1 &  1 & 1 & 1 & 1 & 1 & 1
& 1\\
\hline
$\rho c_{ix}$ & 0 &  1 &  -1 &  0 &  0 &  0 &  0 & 
         1 &  1 &  -1 &   -1 &  1 &  1 &  -1 & -1 & 0 & 0 & 0 & 0
& 3 \\
\hline
$\rho c_{iy}$ & 0 &  0 &  0 &  1 &  -1 &  0 &  0 & 
         1 &  -1 &  1 &   -1 &  0 &  0 &  0 & 0 & 1 & 1 & -1 & -1
& 3\\
\hline
$\rho c_{iz}$ & 0 &  0 &  0 &  0 &  0 &  1 &  -1 & 
         0 &  0 &  0 &   0 &  1 &  -1 &  1 & -1 & 1 & -1 & 1 & -1
& 3\\
\hline
$Q_{ixx}$ & -1 &  2 &  2 &  -1&  -1 &  -1 &  -1 & 
         2 &  2 &  2 &   2 &  2 &  2 &  2 & 2 & -1 & -1 & -1 & -1
& 9/2\\
\hline
$Q_{iyy}$ & -1 &  -1 &  -1 &  2&  2 &  -1 &  -1 & 
         2 &  2 &  2 &   2 &  -1 &  -1 &  -1 & -1 & 2 & 2 & 2 & 2
& 9/2\\
\hline
$Q_{izz}$ & -1 &  -1 &  -1 &  -1&  -1 &  2 &  2 & 
         -1 &  -1 &  -1 &   -1 &  2 &  2 & 2 & 2 & 2 & 2 & 2 & 2
& 9/2\\
\hline
$Q_{ixy}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
          1 &  -1 &  -1 &    1 &  0 &  0 & 0 & 0 & 0 & 0 & 0 & 0
& 9\\
\hline
$Q_{ixz}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
          0 &   0 &   0 &   0 &  1 & -1 & -1 & 1 & 0 & 0 & 0 & 0
& 9\\
\hline
$Q_{iyz}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
          0 &   0 &   0 &   0 &  0 & 0 & 0 & 0 & 1 & -1 & -1 & 1
& 9\\
\hline\hline
$\chi^1$ & 0 &  1 &  1 &  1 &  1 &  -2 &  -2 & 
         -2 &  -2 &  -2 &  -2 &  1 &  1 & 1 & 1 & 1 & 1 & 1 & 1
& 3/4\\
\hline
$\chi^1 \rho c_{ix}$ & 0 &  1 &  -1 &  0&  0 &  0 &  0 & 
         -2 &  -2 &  2 &  2 &  1 &  1 & -1 & -1 & 0 & 0 & 0 & 0
& 3/2\\
\hline
$\chi^1 \rho c_{iy}$ & 0 &  0 &  0 &  1&  -1 &  0 &  0 & 
         -2 &  2 &  -2 &  2 &  0 &  0 & 0 & 0 & 1 & 1 & -1 & -1
& 3/2\\
\hline
$\chi^1 \rho c_{iz}$ & 0 &  0 &  0 &  0&  0 &  -2 &  2 & 
         0 &  0 &  0 &  0 &  1 &  -1 & 1 & -1 & 1 & -1 & 1 & -1
& 3/2\\
\hline
$\chi^2$ & 0 &  1 &  1 &  -1&  -1 &  0 &  0 & 
         0 &  0 &  0 &  0 &  -1 &  -1 & -1 & -1 & 1 & 1 & 1 & 1
& 9/4\\
\hline
$\chi^2 \rho c_{ix}$ & 0 &  1 &  -1 &  0&  0 &  0 &  0 & 
         0 &  0 &  0 &  0 &  -1 &  -1 & 1 & 1 & 0 & 0 & 0 & 0
& 9/2\\
\hline
$\chi^2 \rho c_{iy}$ & 0 &  0 &  0 & -1&   1 &  0 &  0 & 
         0 &  0 &  0 &  0 &   0 &  0 & 0 & 0 & 1 &  1 & -1 & -1
& 9/2\\
\hline
$\chi^2 \rho c_{iz}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
         0 &  0 &  0 &  0 &  -1 &  1 & -1 & 1 & 1 & -1 & 1 & -1
& 9/2\\
\hline
$\chi^3$ & 1 &  -2 &  -2 &  -2&  -2 &  -2 &  -2 & 
         1 &  1 &  1 &  1 &  1 &  1 & 1 & 1 & 1 & 1 & 1 & 1
& 1/2\\
\hline\hline
$w_i$ & 12 & 2 & 2 & 2 & 2 & 2 & 2 & 
1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
& \\
\hline\hline
\end{tabular}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  lb.tex
%
%  Section on lattice Boltzmann hydrodynamics
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

For this work, it is more convenient to rewrite these equations
in tensor notation, where Cartesian coordinates ${x,y,z}$ are
represented by indices $\alpha$ and $\beta$, viz
\begin{equation}
\partial_t \rho + \nabla_\alpha (\rho u_\alpha) = 0
\end{equation}
and
\begin{equation}
\partial_t (\rho u_\alpha) + \nabla_\beta (\rho u_\alpha u_\beta)
= -\nabla_\alpha p
+  \eta \nabla_\beta (u_\alpha \nabla_\beta + \nabla_\alpha u_\beta)
+ \zeta \nabla_\alpha (\nabla_\gamma u_\gamma).
\end{equation}
Here, repeated Greek indices are understood to be summed over.
The conservation law is seem better if the forcing terms of the
right hand side are combined in the fluid stress $\Pi_{\alpha\beta}$
so that
\begin{equation}
\partial_t (\rho u_\alpha) +\nabla_\beta \Pi_{\alpha\beta} = 0.
\end{equation}
In this case the expanded expression for the stress tensor is
\begin{equation}
\Pi_{\alpha\beta} = p \delta_{\alpha\beta} + \rho u_\alpha u_\beta 
+ \eta \nabla_\alpha v_\beta + \zeta (\nabla_\gamma v_\gamma)\delta_{\alpha\beta}
\end{equation}
where $\delta_{\alpha\beta}$ is that of Kroneker. Th Navier-Stokes
equations in three dimensions have 10 degrees of freedom
(or hydrodynamic modes) being
$\rho$, three components of the mass flux $\rho u_\alpha$, and 6 independent
modes from the (symmetric) stress tensor $\Pi_{\alpha\beta}$.

@@

The Navier-Stokes equation may be approximated in a discrete system
by the lattice Boltzmann equation (LBE). A discrete density
distribution function $f_i(\mathbf{r}; t)$ at lattice points $\mathbf{r}$
and time $t$ evolves according to
\begin{equation}
f_i (\mathbf{r} + \mathbf{c}_i \Delta t; t + \Delta t) =
f_i (\mathbf{r}; t) + \sum_j \mathcal{L}_{ij}
\big( f_i(\mathbf{r};t) - f_i^{\mathrm{eq}}(\mathbf{r};t) \big)
\end{equation}
where $\mathbf{c}_i$ is the discrete velocity basis and $\Delta t$
is the discrete time step. The collision operator
$\mathcal{L}_{ij}$ provides the mechanism to compute a discrete
update from the non-equilibrium distribution
$f_i(\mathbf{r}; t)- f_i^\mathrm{eq}(\mathbf{r};t)$. Additional terms
may be added to this equation to represent external body forces,
thermal fluctuations, and so on. These additional terms are discussed
in the following sections.

\subsubsection{The distribution function and its moments}

In lattice Boltzmann, the density and velocity of the continuum fluid
are complemented by the  distribution function
$f_i(\mathbf{r}; t)$ defined with reference to the
discrete velocity space $c_{i\alpha}$.
It is possible to relate the hydrodynamic quatities to the distribution
function via its moments, that is
\begin{equation}
\rho(\mathbf{r};t) = \sum_i f_i(\mathbf{r};t),  \quad
\rho u_\alpha(\mathbf{r};t) = \sum_i f_i(\mathbf{r};t) c_{i\alpha},  \quad
\Pi_{\alpha\beta}(\mathbf{r};t) =
\sum_i f_i(\mathbf{r};t) c_{i\alpha} c_{i\beta}.
\end{equation}
Here, the index of the summation is over the number of discrete
velocities used as the basis, a number which will be denoted
$N_\mathrm{vel}$. For example, in three dimensions
$N_\mathrm{vel}$ is often 19 and the basis is referred to as D3Q19.

The number of moments, or modes, supported by a velocity
set is exactly $N_\mathrm{vel}$, and these can be written in general as
\begin{equation}
M^a(\mathbf{r};t) = \sum_i m_i^a f_i(\mathbf{r};t),
\end{equation}
where the $m_i$ are the eigenvectors of the collision matrix in the LBE.
For example, in the case of the density, all the 
$m_i^a = 1$ and the mode $M^a$ is the density $\rho = \sum_i f_i$. Note
that the number of modes supported by a given basis will generally excceed the
number of hydrodynamic modes; the excess modes have no direct physical
interpretation and are variously referred to as non-hydrodynamic, kinetic,
or ghost, modes.
The ghost modes take no part in bulk hydrodynamics, but may become important
in other contexts, such as thermal fluctuations and near boundaries.
The distribution function can be related to the modes
$M^a(\mathbf{r};t)$ via
\begin{equation}
f_i(\mathbf{r};t) = w_i \sum_a m_i^a N^a M^a(\mathbf{r};t).
\end{equation}
In this equation, $w_i$ are the standard LB weights appearing in the
equilibrium distribution function, while the $N^a$ are a per-mode
normalising factor uniquely determined by the orthogonality condition
\begin{equation}
N^a \sum_i w_i m_i^a m_i^b = \delta_{ab}.
\end{equation}
Writing the basis this way has the advantage that the equilibrium
distribution projects directly into the hydrodynamic modes only.
Putting it another way, we may write
\begin{equation}
f_i^\mathrm{eq} = w_i \big(\rho + \rho c_{i\alpha}u_\alpha / c_s^2
+ (c_{i\alpha} c_{i\beta} - c_s^2\delta_{\alpha\beta})
(\Pi_{\alpha\beta}^\mathrm{eq} - p\delta_{\alpha\beta})/2c_s^4 \big)
\end{equation}
where only (equilibrium) hydrodynamic quantities appear on the right hand side.

\subsubsection{Collision and relaxation times}

\subsection{Model Basis Descriptions}

The D2Q9 model in two dimensions consists one zero vector (0,0), four
vectors of length unity being $(\pm 1,0)$ and $(0, \pm 1)$, and four
vectors of length $\sqrt{2}$ being $(\pm 1, \pm 1)$. The eigenvectors of
the collision matrix, with associated weights and normalisers are shown
in Table~\ref{table-d2q9-spec}.

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|rrrrrrrrr|r|l|}
\hline\hline
$M^a$ & & \multicolumn{9}{c|}{$m_i^a$} & $N^a$  &\\
\hline
$\rho$ & - & 1 &  1 &  1 &  1 &  1 &  1 &  1 &   1 &  1 & 1 &$\mathbf{1}$ \\
\hline
$\rho c_{ix}$ & - & 0 &  1 &  1 & 1 & 0 &  0 & -1 &  1 & -1 & 3 & $c_{ix}$ \\
\hline
$\rho c_{iy}$ & - & 0 & 1 &  0 &  -1 &  1 &  -1 & 1 & 0 & -1 & 3  &$c_{iy}$ \\
\hline
$Q_{xx}$ & 1/3 & -1 &  2 &  2 & 2 & -1 & -1 & 2 & 2 & 2 & 9/2 
& $c_{ix} c_{ix} - c_s^2$ \\
\hline
$Q_{xy}$ & - & 0 &  1 & 0 & -1 & 0 & 0 & -1 & 0 & 1 & 9 & $c_{ix} c_{iy}$ \\
\hline
$Q_{yy}$ & 1/3 & -1 &  2 & -1 & 2 & 2 & 2 & 2 & -1 & 2 & 9/2
& $c_{iy} c_{iy} - c_s^2$ \\
\hline\hline
$\chi^1$ & - &  1 & 4 & -2 & 4 & -2 & -2 & 4 & -2 & 4 & 1/4 & $\chi^1$ \\
\hline
$J_{ix}$ & - & 0 &  4 & -2 & 4 & 0 & 0 & -4 & -2 & -4 & 3/8
& $\chi^1 \rho c_{ix}$\\
\hline
$J_{iy}$ & - & 0 & 4 & 0 & -4 & -2 & 2 & 4 & 0 & -4 & 3/8
& $\chi^1 \rho c_{iy}$\\
\hline\hline
$w_i$ & 1/36 & 16 & 1 & 4 & 1 & 4 & 4 & 1 & 4 & 1 & & $w_i$\\
\hline\hline
\end{tabular}
\end{center}
\caption{TABLE CAPTION}
\label{table-d2q9-spec}
\end{table}

@@

\subsection{Hydrodynamic Boundary Conditions}

\subsubsection{Bounce-Back on Links}

@@

\subsubsection{Fixed objects}

\subsubsection{Moving objects}

@@

\begin{table}
\centering
\tabcolsep=4pt
\begin{tabular}{|l|r|r|rrrrrr|rrrrrrrr|r|l|}
\hline\hline
$M^a$ & & \multicolumn{15}{c|}{$m_i^a$} & $N^a$  &\\
\hline
$\rho$ & - &
 1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &  1 &
1 &$\mathbf{1}$ \\
\hline
$\rho c_{ix}$ & - &
 0 &  1 & -1 &  0 &  0 &  0 &  0 &  1 & -1 &  1 & -1 &  1 & -1 &  1 & -1 &
3  & $c_{ix}$ \\
\hline
$\rho c_{iy}$ & - &
 0 &  0 &  0 &  1 & -1 &  0 &  0 &  1 &  1 & -1 & -1 &  1 &  1 & -1 & -1 &
3  &$c_{iy}$ \\
\hline
$\rho c_{iz}$ & - &
 0 &  0 &  0 &  0 &  0 &  1 & -1 &  1 &  1 &  1 &  1 & -1 & -1 & -1 & -1 &
3  & $c_{iz}$ \\
\hline
$Q_{xx}$ & 1/3 &
-1 &  2 &  2 & -1 & -1 & -1 & -1 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &
9/2  & $c_{ix} c_{ix} - c_s^2$ \\
\hline
$Q_{yy}$ & 1/3 &
-1 & -1 & -1 &  2 &  2 & -1 & -1 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &
 9/2 & $c_{iy} c_{iy} - c_s^2$ \\
\hline
$Q_{zz}$ & 1/3 &
-1 & -1 & -1 & -1 & -1 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &  2 &
 9/2 & $c_{iz} c_{iz} - c_s^2$ \\
\hline
$Q_{xy}$ & - &
 0 &  0 &  0 &  0 &  0 &  0 &  0 &  1 & -1 & -1 &  1 &  1 & -1 & -1 &  1 &
9  & $c_{ix} c_{iy}$ \\
\hline
$Q_{yz}$ & - &
 0 &  0 &  0 &  0 &  0 &  0 &  0 &  1 &  1 & -1 & -1 & -1 & -1 &  1 &  1 &
9  & $c_{iy} c_{iz}$ \\
\hline
$Q_{zx}$ & - &
 0 &  0 &  0 &  0 &  0 &  0 &  0 &  1 & -1 &  1 & -1 & -1 &  1 & -1 &  1 &
9  & $c_{iz} c_{ix}$ \\
\hline\hline
$\chi^1$ & - &
-2 &  1 &  1 &  1 &  1 &  1 &  1 & -2 & -2 & -2 & -2 & -2 & -2 & -2 & -2 &
1/2 & $\chi^1$ \\
\hline
$J_{ix}$ & - &
 0 &  1 & -1 &  0 &  0 &  0 &  0 & -2 &  2 & -2 &  2 & -2 &  2 & -2 &  2 &
3/2 & $\chi^1 \rho c_{ix}$\\
\hline
$J_{iy}$ & - &
 0 &   0 &  0 &  1 & -1 &  0 &  0 & -2 & -2 &  2 &  2 & -2 & -2 &  2 &  2 &
3/2 & $\chi^1 \rho c_{iy}$\\
\hline
$J_{iz}$ & - &
 0 &   0 &  0 &  0 &  0 &  1 & -1 & -2 & -2 & -2 & -2 &  2 &  2 &  2 &  2 &
3/2 & $\chi^1 \rho c_{iz}$\\
\hline
$\chi^3$ & - &
 0 &   0 &  0 &  0 &  0 &  0 &  0 &  1 & -1 & -1 &  1 & -1 &  1 &  1 & -1 &
9 & $c_{ix} c_{iy} c_{iz}$ \\
\hline\hline
$w_i$ & 1/72 &
$16$ & 8 & 8 & 8 & 8 & 8 & 8 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 &
 & $w_i$\\
\hline\hline
\end{tabular}

\caption{Table showing the details of the basis used for the D3Q15 model
in three dimensions. The fifteen modes $M^a$ include two scalar kinetic
modes $\chi^1$ and $\chi^3$, and one vector kinetic mode $J_{i\alpha}$.
The weights in the equilibrium distribution are $w_i$ and the normaliser
for each mode is $N^a$. The eigenvectors of the collision matrix are the
colms of the transformation matrix $m_i^a$. The prefactor $p$ simply
multiplies all elements of $m_i^a$ in that row as a convenience.}
\end{table}

@@

\begin{table}
\centering
\tabcolsep=4pt
\begin{tabular}{|l||r|rrrrrr|rrrr|rrrr|rrrr|r||}
\hline\hline
$M^a$ & \multicolumn{19}{c||}{$m_i^a$} & $N^a$\\
\hline
$\rho $ & 1 &  1 &  1 &  1 &  1 &  1 &  1 & 
         1 &  1 &  1 &   1 &  1 &  1 &  1 & 1 & 1 & 1 & 1 & 1
& 1\\
\hline
$\rho c_{ix}$ & 0 &  1 &  -1 &  0 &  0 &  0 &  0 & 
         1 &  1 &  -1 &   -1 &  1 &  1 &  -1 & -1 & 0 & 0 & 0 & 0
& 3 \\
\hline
$\rho c_{iy}$ & 0 &  0 &  0 &  1 &  -1 &  0 &  0 & 
         1 &  -1 &  1 &   -1 &  0 &  0 &  0 & 0 & 1 & 1 & -1 & -1
& 3\\
\hline
$\rho c_{iz}$ & 0 &  0 &  0 &  0 &  0 &  1 &  -1 & 
         0 &  0 &  0 &   0 &  1 &  -1 &  1 & -1 & 1 & -1 & 1 & -1
& 3\\
\hline
$Q_{ixx}$ & -1 &  2 &  2 &  -1&  -1 &  -1 &  -1 & 
         2 &  2 &  2 &   2 &  2 &  2 &  2 & 2 & -1 & -1 & -1 & -1
& 9/2\\
\hline
$Q_{iyy}$ & -1 &  -1 &  -1 &  2&  2 &  -1 &  -1 & 
         2 &  2 &  2 &   2 &  -1 &  -1 &  -1 & -1 & 2 & 2 & 2 & 2
& 9/2\\
\hline
$Q_{izz}$ & -1 &  -1 &  -1 &  -1&  -1 &  2 &  2 & 
         -1 &  -1 &  -1 &   -1 &  2 &  2 & 2 & 2 & 2 & 2 & 2 & 2
& 9/2\\
\hline
$Q_{ixy}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
          1 &  -1 &  -1 &    1 &  0 &  0 & 0 & 0 & 0 & 0 & 0 & 0
& 9\\
\hline
$Q_{ixz}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
          0 &   0 &   0 &   0 &  1 & -1 & -1 & 1 & 0 & 0 & 0 & 0
& 9\\
\hline
$Q_{iyz}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
          0 &   0 &   0 &   0 &  0 & 0 & 0 & 0 & 1 & -1 & -1 & 1
& 9\\
\hline\hline
$\chi^1$ & 0 &  1 &  1 &  1 &  1 &  -2 &  -2 & 
         -2 &  -2 &  -2 &  -2 &  1 &  1 & 1 & 1 & 1 & 1 & 1 & 1
& 3/4\\
\hline
$\chi^1 \rho c_{ix}$ & 0 &  1 &  -1 &  0&  0 &  0 &  0 & 
         -2 &  -2 &  2 &  2 &  1 &  1 & -1 & -1 & 0 & 0 & 0 & 0
& 3/2\\
\hline
$\chi^1 \rho c_{iy}$ & 0 &  0 &  0 &  1&  -1 &  0 &  0 & 
         -2 &  2 &  -2 &  2 &  0 &  0 & 0 & 0 & 1 & 1 & -1 & -1
& 3/2\\
\hline
$\chi^1 \rho c_{iz}$ & 0 &  0 &  0 &  0&  0 &  -2 &  2 & 
         0 &  0 &  0 &  0 &  1 &  -1 & 1 & -1 & 1 & -1 & 1 & -1
& 3/2\\
\hline
$\chi^2$ & 0 &  1 &  1 &  -1&  -1 &  0 &  0 & 
         0 &  0 &  0 &  0 &  -1 &  -1 & -1 & -1 & 1 & 1 & 1 & 1
& 9/4\\
\hline
$\chi^2 \rho c_{ix}$ & 0 &  1 &  -1 &  0&  0 &  0 &  0 & 
         0 &  0 &  0 &  0 &  -1 &  -1 & 1 & 1 & 0 & 0 & 0 & 0
& 9/2\\
\hline
$\chi^2 \rho c_{iy}$ & 0 &  0 &  0 & -1&   1 &  0 &  0 & 
         0 &  0 &  0 &  0 &   0 &  0 & 0 & 0 & 1 &  1 & -1 & -1
& 9/2\\
\hline
$\chi^2 \rho c_{iz}$ & 0 &  0 &  0 &  0&  0 &  0 &  0 & 
         0 &  0 &  0 &  0 &  -1 &  1 & -1 & 1 & 1 & -1 & 1 & -1
& 9/2\\
\hline
$\chi^3$ & 1 &  -2 &  -2 &  -2&  -2 &  -2 &  -2 & 
         1 &  1 &  1 &  1 &  1 &  1 & 1 & 1 & 1 & 1 & 1 & 1
& 1/2\\
\hline\hline
$w_i$ & 12 & 2 & 2 & 2 & 2 & 2 & 2 & 
1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1
& \\
\hline\hline
\end{tabular}
\caption{Table showing the details of the basis used for the D3Q19 model in
three dimensions. }
\end{table}
